\documentclass{leadsheet-modern}

\begin{document}

\begin{song}[remember-chords,transpose=0]{title={Let Go},composer={Aodhan King, Ben Tan, Laura Toggs},interpret={Hillsong Young\&Free},key={C},tempo={127 bpm}}

\begin{schedule}
I -- S1 -- R -- ZS -- S2 -- R 
\end{schedule}

\begin{intro}
| ^F\_\_\_\_ | ^F\_\_\_\_ |
\end{intro}

\begin{verse}
^F\_~I close my eyes | \_~and colors fly | ^{Am}\_\_~there's no hid- | ^Ging from Your grace. | \\
^F\_~I can't deny | \_~Your heart for mine | ^{Am}\_\_~And it's un- | ^Grelenting chase. | \\
^F\_\_~I was on the | edge of deception, | ^{Am}\_~caught up in my | ^Gown hesitation | \\
^{Dm7}\_~until Your love | ^{C/E}\_~took over me. | ^F\_ \halfrest~ | ^G\_\_
\end{verse}

\begin{chorus}
So I let | ^{Dm7}go~and I let | ^F\_~love show me life | ^{Am}\_like~it's s'posed to | ^Gbe. \\
An oa- | ^{Dm}sis~here awaits | ^F\_~us. \_ All the free- | ^{Am}dom I'll ever | ^Gneed. \\
Now I'm alive | \\
^{Dm}\_Oh la la | ^F\_Oh la la | ^{Am}\_When I let go, | ^G\_then I find life. | \\
^{Dm}\_Oh la la | ^F\_Oh la la | ^{Am}\_When I let go, | ^G\_then I find life. |
\end{chorus}

\begin{interlude}
^{Dm}\_\_\_\_ | ^F\_\_\_\_ | ^{Am}\_\_\_\_ | ^GOh la la la  \\
^{Dm}la\_\_\_| ^F\_\_\_\_ | ^{Am}\_When I let go, | ^G\_then I find life.
\end{interlude}

\begin{verse}
^\_~The higher way | \_~is calling me | ^\_\_to a life | ^unlike before. | \\
^\_~The Father's heart | \_~is beckoning | ^\_\_and I can't | ^resist no more. | \\
^\_\_~Lead me in the | ways of devotion, | ^\_~I~don't wanna get | ^caught in the motions. | \\
^\_~My heart is only | ^for~You Lord. | ^\_ \halfrest~ | ^\_\_
\end{verse}

\end{song}

\end{document}