\documentclass{leadsheet-modern}

\begin{document}

\begin{song}[]{title={Broken Vessels},composer={Joel Houston, Jonas Myrin },interpret={Hillsong},key={G},tempo={70.5
bpm}}

\begin{schedule}
I -- S1 -- B1 -- R -- Solo -- S2 -- B1 -- R -- 4x Solo -- B2 - R
\end{schedule}

\begin{intro}
||: ^{Em}\wholerest~ |^{G}\wholerest~ |^{Em}\wholerest~ |^{G}\wholerest~ :||
\end{intro}

\begin{verse}
All these |^{Em}pieces \_ broken and |^{G}scattered. \\
In mercy |^{Em}gathered \_ mended and |^{G}whole \\
empty |^{Em}handed \_ but not for-|^{G}saken \\
I've been set |^{D} free. \_ I've been set |^{Em} free. ^{D}~\halfrest \\
\end{verse}

\begin{bridge}[numbered=true]
A- |^{C}mazing grace. How |^{D}sweet the sound. \\
That |^{Em}saved a wretch like |^{C}me. \\ 
I |^{C}once was lost. But |^{D}now i am found. \\
Was |^{Em}blind but now I |^{C}see. 
\end{bridge}

\begin{chorus}[numbered=true]
Oh i can see You |^{G}now. |^{D}\wholerest~ \\
Oh i can see the |^{Em}love in Your |^{C}eyes. \\
Laying Yourself |^{G}down. |^{D}\wholerest~ \\
Raising up the |^{Em}broken to |^{C}life. \\
\end{chorus}

\begin{solo}
^{G}\wholerest~ |^{G}\wholerest~ |^{Em}\wholerest~ |^{C}\wholerest~ 
\end{solo}

\begin{verse}
You take our |^{Em}failure \_ You take our |^{G}weakness \\
You set Your |^{Em}treasure \_ In jars of |^{G}clay \\
So take this |^{Em}heart, Lord. \_ I'll be Your |^{G}vessel \\
The world to |^{D}see \_ Your life | ^{Em}in me ^{D}\_
\end{verse}

\begin{bridge}[numbered=true]
A- |^{G}mazing grace. How |^{D}sweet the sound. \\
That |^{Em}saved a wretch like |^{C}me. \\ 
I |^{G}once was lost. But |^{D}now i am found. \\
Was |^{Em}blind but now I |^{C}see. 
\end{bridge}

\end{song}

\end{document}