\documentclass{leadsheet-modern}

\begin{document}

\begin{song}[remember-chords,transpose={0}]{title={Days Gone By},interpret={Hillsong Y\&F},composer={},key={E},tempo={125}}

\begin{schedule}
I - S1 - PC - R - S2 - PC - R - B
\end{schedule}

\begin{intro}
| ^E\_\_ ^{F#m}\_\_ | ^{C#m}\_\_\_\_ |  ^{G#m}\_\_\_\_ | ^{A}\_\_\_\_ | 
\end{intro}

\begin{verse}
^E\_I walked the ^{F#m}world afar |
^{C#m}built up a thousand walls |
^{G#m}To try and hide away | ^A\wholerest | \\
^E\_I searched to ^{F#m}find my soul |
^{C#m}A journey far from home |
^{G#m}Lost in a life I'd | ^Amade

And | ^EI'd been 'round in ^{F#m}circles |
^{C#m}living for the moment | ^{G#m}\_I know I ran so | ^Afar. \\
Was | ^Eacting kind of ^{F#m}crazy |
^{C#m}coming up with empty | ^{G#m}Felt like I lost my | ^Aheart.
\end{verse}

\begin{prechorus}
Now I've | ^B\_found a love | ^{C#m}\_that \_ is | ^Aclearer than the deep blue | ^Eskies. \\
It's true, | ^B\_You were right | ^{C#m}\_there \_ I can see | ^{G#m}it in the days gone | ^Aby. |
\end{prechorus}

\begin{chorus}
^EI\_\_ ^{F#m}\_\_ | ^{C#m}\_\_ ^B\_\_ | ^A\_\_\_  I see | You in the days gone \\
^Eby\_\_ ^{F#m}\_\_ | ^{C#m}\_\_ ^B\_\_ | ^A\_\_\_  Your prom- | ise never left my \\
^Eside. I know some^{F#m}times I tried to | ^{C#m}give up, \_ still You caught | ^{G#m}me~when I fell from | ^Ahigh \\
^EI\_\_ ^{F#m}\_\_ | ^{C#m}\_\_ ^B\_\_ | ^A\_\_\_  I see | You in the days gone \\
^Eby\_\_ ^{F#m}\_\_ | ^{C#m}\_\_\_\_ | ^{G#m}\_\_\_\_ | ^A\_\_\_\_
\end{chorus}

\begin{verse}
^\_You  took  my ^fragile fate | ^\_and  didn’t  hesitate | ^\_Your  love  in  every  scar | ^\_\_\_\_ | \\
^\_Passion  with ^no~restraints | ^\_held back the darkest days. | ^\_So~now my life  is | ^Yours. \\
You’ve  | ^got  me  when  I’m  ^broken You’re | ^with me when I’m hopeless. |
^I~know You’re never | ^far \_ \\
Your | ^mercy has no ^ending it | ^perseveres  unfailing. | ^You’ll  always have  my | ^heart.
\end{verse}

\begin{bridge}
||: See | ^AYou in the ^{E/G#}days gone | ^Aby. :||
^A\_\_\_\_ | \_\_ And I need | You everyday 'cause |
\end{bridge}


\end{song}

\end{document}


