\documentclass{leadsheet-modern}

\begin{document}

\begin{song}[remember-chords,transpose=0]{title={Do It Again},composer={Steven Furtick, Matt redman, Chris Brown, Mack Brock},interpret={Elevation worship},key={A},tempo={86 bpm}}

\begin{schedule}
I -- S1 -- R -- S -- S2 -- R -- R -- B -- ZS
\end{schedule}

\begin{intro}
||: ^{D}\_\_\_\_ | \_\_\_\_ | ^{A/C#}\_\_\_\_ | \_\_\_\_ :||
\end{intro}

\begin{verse}
| ^{D}\_\_Walking around | these walls \_\_ | ^{A/C#}\_\_I~thought by now | they’d fall \_\_ \\
| ^D\_\_but~You have nev- | er failed me yet. | ^A\_\_\_\_ | \_\_\_\_ \\
| ^D\_\_Waiting for change | to come \_\_ | ^{A/C#}\_\_~knowing the bat- | tle’s won \_\_ \\
| ^D\_\_for You have nev- | er failed me yet. | ^A\_\_\_\_ | \_\_\_\_ \\
\end{verse}

\begin{chorus}
| ^D\_~Your promise still | ^Estands, \_ great is Your faith- | ^Afulness, faith- | ^Dfulness. \\
| ^D\_~I’m still in Your | ^Ehands. \_ This is my con- | ^Afidence, You’ve nev- | ^Der failed (me yet). 
\end{chorus}

\begin{solo}
| ^A\_\_\_\_ | ^D\_\_\_\_ | ^A\_\_\_\_ | ^D\_\_\_\_ |
\end{solo}

\begin{verse}
| ^\_\_I know the night | won’t last \_\_ | ^\_\_Your~word will come | to pass \_\_ \\
| ^\_\_My~heart will sing | Your praise again | ^\_\_\_\_ | \_\_\_\_ \\
| ^\_\_Jesus You’re still | enough. \_\_ | ^\_\_ Keep me within | Your love. \_\_ \\
| ^\_\_My heart will sing | Your praise again | ^\_\_\_\_ | \_\_\_\_ \\
\end{verse}

\begin{bridge}
||: ^D\_I’ve seen You mov^{A/C#}e ^D\_ | \_You move the moun^{E/G#}\_~tains ^A\_ | \_and I believe ^{E/G#} ^A\_ \\
| I’ll see You do ^{A/C#}it a^Dgain | You made a wa^{A/C#}y\_ ^D\_ | Where there was no ^{E/G#}\_way, ^A\_ \\
| and I belie^{E/G#}ve ^A\_ | \_I’ll see You do ^{A/C#}it a-^Dgain. :||
\end{bridge}


\begin{interlude}
| ^D\_\_ ^{A/C#}\_ ^D\_ | \_\_I'll see You do ^{E/G#}it a^Again | \_\_^{E/G#}\_ ^A\_ \\
| \_\_^{A/C#}\_ ^D\_ | \_\_^{A/C#}\_ ^D\_ | \_\_^{E/G#}\_ ^A\_ | \_\_^{E/G#}\_ ^A\_ | \_\_\_\ | \_\_\_\_
\end{interlude}

\end{song}

\end{document}

Bridge

|3x|
Tag

REPEAT CHORUS 
|2x|
Turnaround
You’ve never failed me 
yet
I 
never will forget 
You’ve 
never failed me yet 
I 
never will forget 
 
