\documentclass[]{leadsheet}

\begin{document}

\begin{song}[remember-chords]{title={Glory come Down},composer={Jason Upton},interpret={Jason Upton},key={G}}

\begin{schedule}
\songpart{I}
\songpart{V1}
\songpart{R}
\songpart{V2}
\songpart{R}
\songpart{B}
\songpart{B}
\songpart{B}
\songpart{R}
\songpart{R}
\songpart{O}
\end{schedule}

\begin{intro}
|:^{Em}\wholerest~ | ^{D2/E}\wholerest~ :| 
\end{intro}

\begin{verse}
|^{Em}\quarterrest~Father, listen to our |^{G/B}ear-nest ^{C}prayer. \quarterrest~ \\
|^{Em}\quarterrest~Jesus prayed\_ it ^{D/F#}years a- |^{G}go.\_\_\_\quarterrest~ \\
|^{C}\quarterrest~That the glo-ry You had gi- |^{Dsus}ven Him ^{D}\_ \\
|^{C}\quarterrest~We would some-how come to know. |^{Bsus}\_\_\_ ^{B}\quarterrest~ \\
|^{Em}\quarterrest~Make us one\_ acc-ording to |^{G/B}\_ Your ^{C}plan\_\_, \\
|^{Em}\quarterrest~As in hea-ven it ^{D/F#}will be. |^{G}\_\_\_\_ \\
^{C}\quarterrest~Fill us with\_ the truth and right- |^{Dsus}eous-ness\_ ^{D}\quarterrest~ \\
|^{C}\quarterrest~You de-sire\_ the world to see |^{Bsus}\_\_ ^{B}\_  
\end{verse}

\begin{chorus}
Let Your |^{Em}glo- ^{C}ry\_\_ |^{D/F#}and ho- ^{G}nor\_\_
|^{Em}\quarterrest~ Fall ^{C}on\_ our face |^{Dsus}\_\_ ^{D}\_\_. \\
|^{Em}Ho- ^{C}ly\_\_ |^{D/F#}Fath- ^{G}er\_\_,
|^{C}\quarterrest~ Rest in ^{Dsus}\_ this place |^{Em}\_\_\_\_ .
\end{chorus}

\begin{verse}
|^\eighthrest~The church is sick\_ in need of God |^\_a- ^lone\_\_ \\
|^\quarterrest~peo-ple we\_ must seek ^His\_ face. |^\_\_\_\quarterrest~ \\
|^\quarterrest~If we turn\_ from all our un-right- |^eous- ^ness\_\_\_ \\
|^\quarterrest~He'll for-give\_ our e-vil ways. |^\_\_ ^\_\halfrest~ \\
|^\quarterrest~May the eyes\_ of God be on |^\_us ^here.\_\_ \\
|^\quarterrest~Lord, re-vive\_ us by ^\_ Your grace. |^\_\_\_\_ \\
|^\quarterrest~Ho-ly Spi-rit be for-e- |^ver near, ^\_\_\_ \\
|^\quarterrest~Sa-tu-rate\_ us in this place. |^\_\_ ^\_
\end{verse}

\begin{bridge}
|:^{Em}Let the fire fall. 
Let the ^{D/F#}wind blow. 
Let the |^{G}glo-ry come down. \halfrest~ :|
\end{bridge}

\begin{outro}
|^{C}\quarterrest~ Rest in ^{Dsus}\_ this place |^{Em}\_\_\_\_ .
|^{C}\quarterrest~ Rest in ^{Dsus}\_ this place |^{Em}\_\_\_\_ .
\end{outro}

\end{song}
\end{document}

