\documentclass[]{leadsheet}

\useleadsheetslibrary{musicsymbols}

\begin{document}

\begin{song}[remember-chords,transpose={0}]{title={Lifeline},interpret={Hillsong Young and Free},composer={Michael Fatkin, Joel Houston, Melodie Wagner, Renee Sieff},key={G},tempo={ bpm}}

\begin{schedule}
I -- R -- S1 -- R -- S2 -- R -- B -- R -- O 
\end{schedule}

\begin{intro}
| ^C\wholerest~ | ^{Em}\wholerest~ | ^D\wholerest~
\end{intro}

\begin{chorus}
| ^{Bm7}\_\_ You took me from the | ^{C}wayside, called me Your | ^{Em7}own. \\
Throwing me Your | ^{D}lifeline, You carried me | home \\
^{Bm7}Jesus, You're all | ^{C}\_~I want, You're all | ^{Em}\_~I want | ^D\_\_ | \\
\_ ^{Bm7}Over the ho- | ^{C}rizon is where I look be- | ^{Em7}yond, \\
You're the silver | ^{D}linung breaking through the | \_ strom. \\
^{Bm7}Jesus, You're all | ^{C}\_~I~want, You're all | ^{Em}\_~I~want | ^D\_\_
\end{chorus}

\begin{verse}
\_ ^{Bm7}\_~A | ^{C}castaway lost in a | ^{Em}viloent sea, | ^{D}drifting away 'til You | resuced me. | \\
^{C}\_~You ser my feet | ^{Em7}on~solid ground. | ^{D}\_\_ | \_\_ \\
When I | ^{C}lost my grip, love | ^{Em7}held on tight, | ^{D}even my worst didn't | change Your mind. | \\
^{C}\_~My guilt and shame | ^{Em7}lost in Your grace. | ^{D}\_\_ 
\end{verse}

\begin{verse}
\_ ^\_~A | ^runaway heart in a | ^distant land, I | ^wandered so far, still to| find You there. | \\
^\_~There's no esca- | ^ing~Your embrace. | ^\_\_ | \_\_ \\
With my | ^hope locked in and | ^future sure, my | ^life has a cause worth | fighting for. | \\
^\_~My soul exists | ^\_~to know Your Name. | ^\_\_ 
\end{verse}

\begin{bridge}
^{Bm7}\_~And | ^{Am}oh | \_ ^{Am/B}You~are my | ^Chope | \_\_ |
^{Em}Jesus forever | You've for- | ^Dgiven my failures | \_
You are my | ^{Am}hope You never let | ^Cgo | \_\_ |
^{Em}Jesus forever | You've for- | ^Dgiven my failures | \_
You are my | ^Chope | \_\_ | \_\_ |
\end{bridge}

\begin{outro}
| You're all ^{Bm7}I~want | ^C\_\_ | ^{Em}\_\_ | ^D\_\_ | \_\_ | ^C\_\_
\end{outro}
\end{song}
\end{document}