\documentclass{leadsheet}

\begin{document}

\begin{song}[remember-chords=true,transpose=+3]{title={Love The Lord},composer={Lincoln Brewster},interpret={Lincoln Brewster},key={E},tempo={97 bpm}}

\begin{schedule}
I -- V1 -- R1 -- V2 -- R2 -- B -- R2
\end{schedule}

\begin{intro}
|:^{E}\halfrest~ ^{B}\halfrest~ | ^{C#m}\halfrest~ ^{E/G#}\halfrest~ | ^{A}\halfrest~ \quarterrest~ ^{B}\quarterrest~ | ^{E}\halfrest~ ^{B}\quarterrest~ ^{A}\quarterrest~ :|
\end{intro}

\begin{verse}
|^{E}Love the Lord, your God. ^{B}\eighthrest~ with all your heart,\\
|^{C#m}\eighthrest~ with all your ^{E/G#}soul, with all your mind,\\
|^{A}\quarterrest~ and with all ^{B}your strength. | ^{E}\halfrest~ ^{B}\quarterrest~ ^{A}\quarterrest~ \\
|^{E}Love the Lord, your God. ^{B}\eighthrest~ with all your heart,\\
|^{C#m}\eighthrest~ with all your ^{E/G#}soul, with all your mind,\\
|^{A}\quarterrest~ and with all ^{B}your strength. | ^{E}\halfrest~
\end{verse}

\begin{chorus}[numbered]
\eighthrest~ With all your heart, | ^{A}\halfrest~ with all your soul,
| ^{B}\halfrest~ with all your mind, \\
|^{A/C#}\halfrest~ with all your strength. | ^{B/D#}\halfrest~ | ^{E}Love the Lord, your God,\\
^{B}\eighthrest~ with all your heart, | ^{C#m}\halfrest~ with all your soul, ^{E/G#}\eighthrest~ with all your mind, \\
| ^{A}\quarterrest~ and with all ^{B}your strength. | ^{E}\halfrest~ ^{B}\quarterrest~ ^{A}\quarterrest~ \\
\end{chorus}

\begin{verse}
|^I will serve the Lord. ^\eighthrest~ with all my heart,\\
|^\eighthrest~ with all my ^soul, with all my mind,\\
|^\quarterrest~ and with all ^my strength | ^\halfrest~ ^\quarterrest~ ^\quarterrest~ \\
|^I will serve the Lord. ^\eighthrest~ with all my heart,\\
|^\eighthrest~ with all my ^soul, with all my mind,\\
|^\quarterrest~ and with all ^my strength | ^\halfrest~ \\
\end{verse}

\begin{chorus}[numbered]
\eighthrest~ With all my heart, | ^\halfrest~ with all my soul,
| ^\halfrest~ with all my mind, \\
|^\halfrest~ with all my strength. | ^\halfrest~ | ^I will serve the Lord,,\\
^\eighthrest~ with all my heart, | ^\halfrest~ with all my soul, ^\eighthrest~ with all my mind, \\
| ^\quarterrest~ and with all ^my strength. | ^\halfrest~ ^\quarterrest~ ^\quarterrest~ \\
\end{chorus}

\begin{bridge}
|^{E}I will | love You. |^{A}I will | love You.\\
|^{C#m7}I will | praise You |^{A} I will praise You.\\
|^{E}I will | serve You, Lord. |^{A} I will serve You.\\
|^{C#m7}I will | trust You, Lord. |^{A} I will trust You.\\
\end{bridge}

\end{song}

\end{document}