\documentclass{leadsheet-modern}

\useleadsheetslibrary{musicsymbols}

\begin{document}

\begin{song}[remember-chords,transpose={7}]{title={My Lighthouse},interpret={Rend Collective},composer={Rend Collective},key={C},tempo=110}

\begin{schedule}
I -- V1 -- PC -- V2 -- PC -- R -- V3 -- PC -- R -- B -- B -- B -- R -- R
\end{schedule}

\begin{intro}
| \meter{4}{4} ^{C}\wholerest~ | ^{C}\wholerest~ ||
\end{intro}

\begin{verse}
| ^{C}In my wrest- ling, and | ^{F2}in~my ^{C}doubts, \quarterrest~
| ^{F2}in~my ^{C}fail- ures, You | ^{Gsus}won't walk out. \quarterrest~ \\
| ^{C}Your great love will \quarterrest~ | ^{F2}lead me ^{C}through; \quarterrest~ 
\end{verse}

\begin{prechorus}
| ^{F2}\eighthrest~You are the ^{C/E}peace\_ in my | ^{Gsus}trou- bled ^{C}sea, whoa oh, \\
| ^{F2}\eighthrest~You are the ^{C/E}peace\_ in my | \meter{2}{4} ^{Gsus}trou- bled | \meter{4}{4} ^Csea. \halfrest~ | \wholerest~
\end{prechorus}

\begin{verse}
| ^In the si-lence, You | ^won't let ^go, \quarterrest~
| ^in the ^ques- tions,\_ Your | ^truth will hold. \quarterrest~ \\
| ^Your great love will \quarterrest~ | ^lead me ^through; \quarterrest~
\end{verse}

\begin{chorus}
| ^{F2}My Lighthouse, ^{C}\_ \quarterrest~ | ^{Am7}my~Lighthouse. ^{Gsus}\_~\quarterrest~ \\
| ^{F2}shining in the dark-^{C}ness, \quarterrest~
| ^{Am7}I~will follow You!. ^{Gsus}Oh,~\quarterrest~ \\
| ^{F2}my Lighthouse, ^{C}\_ \quarterrest~ | ^{Am7}my~Lighthouse. ^{Gsus}\_~\quarterrest~ \\
| ^{F2}I~will trust the prom-^{C}ise: \quarterrest~
| ^{Am7}you will carry me ^{Gsus}\_  \\
safe to | ^{F2}shore, \_\_ ^{C}\_\_ | ^{G}\_ \quarterrest~ safe to | ^{F2}shore, \_\_ ^{C}\_\_ | ^{G}\_ \quarterrest~ \\ safe to | ^{F2}shore, \_\_ ^{C}\_\_ | ^{G}\_ \quarterrest~ safe to |^{C}shore. \quarterrest~\halfrest~ | \wholerest~ ||
\end{chorus}

\begin{verse}
| ^I won't fear what\_ to- | ^morrow ^brings. \quarterrest~
| ^With each ^morning, I'll | ^rise and\_ sing. \quarterrest~ \\
| ^My God's love will \quarterrest~ | ^lead me ^through. \quarterrest~
\end{verse}

\begin{bridge}
| ^{F2}\eighthrest~Fire\_ be ^{C}fore-us,
| ^{Am7}\eighthrest~Youre're\_ the ^{G}bright-est, \\
| ^{F2}\eighthrest~You will ^Clead us | ^{Am7}through the ^Gstorms. |
\end{bridge}

\end{song}
\end{document}
#t 