\documentclass[]{leadsheet}

\begin{document}

\begin{song}[remember-chords,transpose=+3]{title={Offering (Christmas Version)},interpret={Paul Baloche},composer={Paul Baloche},key={D}}

\begin{schedule}
\songpart{I}
\songpart{V1}
\songpart{R}
\songpart{Z}
\songpart{V2}
\songpart{R}
\songpart{R}
\songpart[inst]{O}
\songpart[8x]{O}

\end{schedule}

\begin{intro}
|:^{D}\wholerest~ |^{A/D}\halfrest~ ^{D}\halfrest~ |^{G}\wholerest~ | \wholerest~ :|
\end{intro}

\begin{verse}
| ^{D}\quarterrest~ Over the | ^{A/C#}skies of Bethle- | ^{G/B}hem appeared a | ^{D/A}star \\
| ^{D/F#}\quarterrest~ While angels | ^{G}sang to lowly she- | ^{A7sus4}pherds | \wholerest~ \\
| ^{D}\quarterrest~ Three wise men | ^{A/C#}seeking truth \quarterrest~ | ^{G/B}traveled from a- | ^{D/A}far \\
| ^{D/F#}\quarterrest~ Hoping to | ^{G}find the child from | ^{A7sus4}Heaven | \wholerest~ \\
| ^{G/B}Falling ^{A7/C#}on their | ^{D}knees
They | ^{F#}bowed be- ^{F#7/A#}fore the | ^{Bm}humble | ^{A}Prince ^{G}of | ^{D}Peace
\end{verse}

\begin{verse}
| ^\quarterrest~ The sun can- | ^not compare to the | ^glory of Your | ^love. \\
| ^\quarterrest~ There is no sha- | ^dow in Your pres- | ^ence. | \wholerest~ \\
| ^\quarterrest~ No mortal | ^man would dare to | ^stand before Your | ^throne, \\
| ^\quarterrest~ Before the | ^Holy One of | ^heaven. | \wholerest~ \\
It's | ^only ^by Your | ^blood 
And it's | ^only  ^through Your | ^mercy | ^Lord ^I co- | ^me. 
\end{verse}

\begin{chorus}
| ^{D/F#}\quarterrest~ I bring an of- | ^{G}fering of wor- | ^{A7sus4}ship to my King | ^{D}\wholerest~ \\
| ^{D/F#}\quarterrest~ No one on | ^{G}earth deserves the prai- | ^{A7sus4}ses that I | ^{D}sing. \\
| ^{D/F#}\quarterrest~ Jesus may | ^{G}You receive the | ^{A7sus4}honor that You're | ^{E}due. | \halfrest~ \quarterrest~ \\
O | ^{Gmaj7}Lord, I bring an of- | ^{A7sus4}fering to Y- | ^{D}ou. 
\end{chorus}

\begin{interlude}
|^{A/C#}\halfrest~ ^{D}\halfrest~ |^{G/B}\halfrest~ I bring an of- | fering to Y- | ^{D}ou. |^{A/C#}\halfrest~ ^{D}\halfrest~ |^{G/B}\wholerest~ |\wholerest~ 
\end{interlude}

\begin{outro}
|: ^{D}\quarterrest~ We bring an of- | ^{D/F#}fering to you | ^{G}\_ |^{Bb}Oh - ^{C}o :| 
\end{outro}

\end{song}

\end{document}

