\documentclass{leadsheet-modern}

\newversetype{chorus2}[ name=Refrain 2, named=true, after-label= ]

\begin{document}

\begin{song}[remember-chords,transpose=0]{title={Rooftops},short-title={Rooftops},interpret={Jesus Culture},lyrics={Jesus Culture},composer={Jesus Culture},key={E},tempo={100 bpm}}

\begin{schedule}
 I -- R1 -- V1 -- R2 -- V2 -- R2 -- B -- R2 -- R2
\end{schedule}

\begin{intro}
|: ^{C#m}\wholerest~ | \wholerest~ |^{A}\wholerest~ | \wholerest~ :|
\end{intro}


\begin{verse}     
|^{C#m}\halfrest~ Here I am | before You, |^{B}falling in love and seek- | ing Your truth, \\ 
|^{Amaj7}knowing that Your perfect grace |\halfrest~ \quarterrest~ \eighthrest~ has |^{Bsus}brought me to this place. | \halfrest~ \quarterrest~ \eighthrest~ \\
Be- |^{C#m}cause of You I free- | ly live. My |^{B}life to You, oh God | I give. \\
So, I |^{F#m}stand before You God, |^{C#m}\halfrest~ \quarterrest~ I lift |^{E}~my voice 'cause You set |^{Bsus}me free. | \halfrest
\end{verse}

\begin{chorus}
So, I | ^{E}shout out Your name | \halfrest~ \eighthrest~ from the roof- | ^{B}tops \\
I proclaim | \halfrest~ \eighthrest~ that I am | ^{C#m}Yours | \halfrest~ I am | ^{A}Yours. | ^{F#m}\wholerest~
\end{chorus}

\begin{verse}
|^All the good You've done | for me, I | ^lift up my hands for all | to see \\
You're the | ^only one | \halfrest~ \quarterrest~ \eighthrest~ who | ^brings me to my knees | \halfrest~ \quarterrest~ \eighthrest~ \\
to | ^share this love across | the earth the | ^beauty of Your ho- | ly worth. \\
So I | ^kneel before You God | ^\halfrest~ \quarterrest~ I lift | ^my hands 'cuz You set | ^me free
\end{verse}

\begin{chorus2}
So, I | ^{E}shout out Your name | \halfrest~ \eighthrest~ from the roof- | ^{B}tops \\
I proclaim | \halfrest~ \eighthrest~ that I am | ^{C#m}Yours | \halfrest~ I am | ^{A}Yours. | \wholerest~ \\
| ^{E}All that I am  | \halfrest~ \eighthrest~ I place into- | ^{B}Your loving hands, \\
| \halfrest~ \eighthrest~ and I am | ^{C#m}Yours | \halfrest~ I am | ^{Amaj7}Yours. | \wholerest~
\end{chorus2}

\begin{bridge}
|: \halfrest~ \quarterrest~ Here I am, | ^{E}I stand with arms | wide open to the One, \\
| ^{C#m}\quarterrest~ the Son, the e- | verlasting God, | ^{A}\halfrest~ \quarterrest~ the e- | verlasting God | ^{F#m}\wholerest~ :|
\end{bridge}

\end{song}
\end{document}