\documentclass{leadsheet}

\begin{document}

\begin{song}[remember-chords]{title={You make me brave},composer={Amanda Cook},interpret={Bethel},key={Eb},tempo={134 bpm}}

\begin{schedule}
I -- Z -- V1 -- R -- Z -- V2 -- R -- R -- B -- B -- R -- I
\end{schedule}

\begin{intro}
|| \wholerest~ | \wholerest~ || \wholerest~ | \wholerest~ || 
\end{intro}

\begin{interlude}
||^{Ab}\wholerest~ |^{Fm7}\wholerest~ |^{Eb/G}\wholerest~ |^{Eb}\wholerest~ 
|^{Ab}\wholerest~ |^{Fm}\wholerest~ |^{Eb}\wholerest~ |^{Eb}\wholerest~ ||
\end{interlude}

\begin{verse}
I |^{Cm}stand \_ be- |^{Ab}fore You |^{Eb}now |\_ \\
The |^{Cm}greatness of |^{Ab}Your re- |^{Eb}nown \\
I have |^{Cm}heard \_ of the |^{Ab}majesty and |^{Eb}wonder of |^{Bb}You \\
King of |^{Cm}Hea- ven in humi- |^{Ab}lity I |^{Fm}bow |\_
\end{verse}

\begin{chorus}
As (to) Your |^{Eb}love in wave ^{Cm}after |^{Bb}wave |
Crashes ^|{Fm}over |^{Eb/G}me, crashes |^{Ab}over |^{Bb}me \\
For You are |^{Eb}for us | You are ^{Cm}not |^{Bb}against us |
Champion of |^{Fm}Heaven
You |^{Eb/G}made a way for |^{Ab}all to |^{Bb}enter in (to Your love)
\end{chorus}

\begin{verse}
I have |^heard You cal- |^ling my |^name |\_ \\
I have |^heard the song of |^love that You |^sing |\_ \\
So I will |^let You draw me |^out beyond the |^shore \\
Into Your |^grace, |^\_ your |^,grace |^\_
\end{verse}

\begin{bridge}[numbered=true]
|You make me |^{Cm}brave. | You make me |^{Ab}brave. \\
|You call me |^{Eb/G}out beyond the shore|\_  into the |^{Bb}waves \\
|You make me |^{Cm}brave.  | You make me |^{Ab}brave. \\
|No fear can |^{Eb/G}hinder now the Love|\_  that made a |^{Bb}way |\_ |
\end{bridge}

\begin{bridge}[numbered=true]
|You make me |^brave. | You make me |^brave. \\
|You call me |^out beyond the shore|^\_ into the |^waves \\
|You make me |^brave. You make me |^brave. \\
|No fear can |^hinder now the promises You've made
\end{bridge}

\begin{outro}
Champion of Heaven
You made a way for all to enter in
\end{outro}

\end{song}

\end{document}